We are not the 99 percent: quantifying asphericity in the distribution of Local Group satellites

### 2018-01-31 paper/paper.tex
edit

Figure \ref{fig:scatter_width} summarizes the results for the plane
width distributions.
The panel on the left compares the results for the MW and M31
observations against its randomized version. 
The most interesting outcome is that the MW plane width is smaller
than $\approx 98\%$ of the planes computed from the randomized distribution,
while the M31 plane width is consistent with the same distribution.

>>>>

Figure \ref{fig:scatter_width} summarizes the results for the width
measurements.
The left panel compares the results for the MW and M31
observations (stars) against its spherically randomized satellites.
The most interesting outcome is that the MW plane width is smaller
than $\approx 98\%$ of the planes computed from the randomized distribution,
while the M31 plane width is only slightly smaller than the average of
the distribution.

The middle panel in \ref{fig:scatter} compares the observational resul
against the measurements of all pairs from the Illustris1-Dark
simulation.
In this case we have a similar result as before. 
The observed MW width is smaller than all the results in the
simulation, there is not a single halo with similar values.
On the other hand, the results for the M31 are entirely consistend
with observations. Most of the halos in the simulation show a width
value similar to M31.

The right panel.
